---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

This is an exploratory study via logistic regressions

```{r}
library(caret)
library(glmnet)
```

```{r}
action_count <- read.table(file='../data/beerslaw/logistic_regression/action_count.tsv', header=TRUE, sep='\t')
```

# General Logistic Regression
We start with a general Logistic regression.
```{r}
general_model <- glm(
      formula = binconcepts ~ 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(general_model)
general_coeffs = coef(general_model)
boxplot(
  general_coeffs, 
  xlab='general model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#7389AE'
)
```


# Simple Demographics
## Language
Language had a great discrepancy in the predictive task
```{r}
language_model <- glm(
      formula = binconcepts ~ 
                french + german +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(language_model)
language_coeffs = coef(language_model)

language_coeffs = coef(language_model)
boxplot(
  language_coeffs, 
  xlab='language model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#0C1618'
) 
abline(h=language_coeffs['french'])

```

### French
```{r}
language_model <- glm(
      formula = binconcepts ~ 
                french +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(language_model)
```

### German
```{r}
german_model <- glm(
      formula = binconcepts ~ 
                german +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(language_model)

german_coeffs = coef(german_model)
boxplot(
  german_coeffs, 
  xlab='german model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#0C1618'
) 
abline(h=german_coeffs['german'])
```


## Field
```{r}
field_model <- glm(
      formula = binconcepts ~ 
                chemistry + textiles + biology + fast + pharma + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(field_model)

field_coeffs = coef(field_model)
boxplot(
  field_coeffs, 
  xlab='field model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#004643'
) 
abline(h=field_coeffs['chemistry'], col='#004643')
abline(h=field_coeffs['textiles'], col='#004643')
abline(h=field_coeffs['biology'], col='#004643')
abline(h=field_coeffs['fast'], col='#004643')
abline(h=field_coeffs['pharma'], col='#004643')
```


## Year
```{r}
year_model <- glm(
      formula = binconcepts ~ 
                firsty + secondy + thirdy + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(year_model)

year_coeffs = coef(year_model)
boxplot(
  year_coeffs, 
  xlab='year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=year_coeffs['firsty'], col='#3F7267')
abline(h=year_coeffs['secondy'], col='#3F7267')
abline(h=year_coeffs['thirdy'], col='#3F7267')

```
### First Year
```{r}
firsty_model <- glm(
      formula = binconcepts ~ 
                firsty + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(firsty_model)

firsty_coeffs = coef(firsty_model)
boxplot(
  firsty_coeffs, 
  xlab='first year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=firsty_coeffs['firsty'], col='#3F7267')

```

### Second Year
```{r}
secondy_model <- glm(
      formula = binconcepts ~ 
                secondy +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(secondy_model)

secondy_coeffs = coef(secondy_model)
boxplot(
  secondy_coeffs, 
  xlab='second year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=secondy_coeffs['secondy'], col='#3F7267')

```

### Third Year
```{r}
thirdy_model <- glm(
      formula = binconcepts ~ 
                thirdy + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(thirdy_model)

thirdy_coeffs = coef(thirdy_model)
boxplot(
  thirdy_coeffs, 
  xlab='third year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=thirdy_coeffs['thirdy'], col='#3F7267')

```

### First Year and Third Year
```{r}
firstthree_model <- glm(
      formula = binconcepts ~ 
                firsty + thirdy +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(firstthree_model)

firstthree_coeffs = coef(firstthree_model)
boxplot(
  firstthree_coeffs, 
  xlab='first and third year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=firstthree_coeffs['firsty'], col='#3F7267')
abline(h=firstthree_coeffs['thirdy'], col='#3F7267')
```
### First and Second
```{r}
firstsecond_model <- glm(
      formula = binconcepts ~ 
                firsty + secondy +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(firstsecond_model)

firstsecond_coeffs = coef(firstsecond_model)
boxplot(
  firstsecond_coeffs, 
  xlab='first and second year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=firstsecond_coeffs['firsty'], col='#3F7267')
abline(h=firstsecond_coeffs['secondy'], col='#3F7267')
```

### Second and third year
```{r}
secondthird_model <- glm(
      formula = binconcepts ~ 
                secondy + thirdy +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(secondthird_model)

secondthird_coeffs = coef(secondthird_model)
boxplot(
  secondthird_coeffs, 
  xlab='second and third year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#3F7267'
) 
abline(h=secondthird_coeffs['thirdy'], col='#3F7267')
abline(h=secondthird_coeffs['secondy'], col='#3F7267')
```

## Gender
```{r}
gender_model <- glm(
      formula = binconcepts ~ 
                male + female + other +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(gender_model)

gender_coeffs = coef(gender_model)
boxplot(
  gender_coeffs, 
  xlab='gender model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#7D9D8B'
) 
abline(h=gender_coeffs['male'], col='#7D9D8B')
abline(h=gender_coeffs['female'], col='#7D9D8B')
abline(h=gender_coeffs['other'], col='#7D9D8B')
```
### Female
```{r}
female_model <- glm(
      formula = binconcepts ~ 
                female +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(female_model)

female_coeffs = coef(female_model)
boxplot(
  female_coeffs, 
  xlab='female model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#7D9D8B'
) 
abline(h=female_coeffs['female'], col='#7D9D8B')
```

```{r}
male_model <- glm(
      formula = binconcepts ~ 
                male + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(male_model)

male_coeffs = coef(male_model)
boxplot(
  male_coeffs, 
  xlab='male model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#7D9D8B'
) 
abline(h=male_coeffs['male'], col='#7D9D8B')
```

# Double Demographics
## Language & Year
```{r}
LY_model <- glm(
      formula = binconcepts ~ 
                french + german + firsty + secondy + thirdy +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(LY_model)


LY_coeffs = coef(LY_model)
boxplot(
  LY_coeffs, 
  xlab='language & year model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#FAF4D3'
) 
abline(h=LY_coeffs['french'], col='#FAF4D3')
abline(h=LY_coeffs['german'], col='#FAF4D3')
abline(h=LY_coeffs['thirdy'], col='#FAF4D3')
abline(h=LY_coeffs['firsty'], col='#FAF4D3')
abline(h=LY_coeffs['secondy'], col='#FAF4D3')
```

## Language & Gender
```{r}
LG_model <- glm(
      formula = binconcepts ~ 
                french + german + female + male + other + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(LG_model)

LG_coeffs = coef(LG_model)
boxplot(
  LG_coeffs, 
  xlab='language & gender model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#E6D06A'
) 
abline(h=LG_coeffs['french'], col='#E6D06A')
abline(h=LG_coeffs['german'], col='#E6D06A')
abline(h=LG_coeffs['female'], col='#E6D06A')
abline(h=LG_coeffs['male'], col='#E6D06A')
abline(h=LG_coeffs['other'], col='#E6D06A')
```

## Language and Field
```{r}
LF_model <- glm(
      formula = binconcepts ~ 
                french + german + chemistry + textiles + biology + fast + pharma + 
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(LF_model)

LF_coeffs = coef(LF_model)
boxplot(
  LF_coeffs, 
  xlab='language & field model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#DCBE35'
) 
abline(h=LF_coeffs['french'], col='#DCBE35')
abline(h=LF_coeffs['german'], col='#DCBE35')
abline(h=LF_coeffs['chemistry'], col='#DCBE35')
abline(h=LF_coeffs['textiles'], col='#DCBE35')
abline(h=LF_coeffs['biology'], col='#DCBE35')
abline(h=LF_coeffs['fast'], col='#DCBE35')
abline(h=LF_coeffs['pharma'], col='#DCBE35')
```

## Year & Gender
```{r}
YG_model <- glm(
      formula = binconcepts ~ 
                firsty + secondy + thirdy + male + female + other +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(YG_model)

YG_coeffs = coef(YG_model)
boxplot(
  YG_coeffs, 
  xlab='year & gender model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#DCBE35'
) 
abline(h=YG_coeffs['firsty'], col='#D1AC00')
abline(h=YG_coeffs['secondy'], col='#D1AC00')
abline(h=YG_coeffs['thirdy'], col='#D1AC00')
abline(h=YG_coeffs['female'], col='#D1AC00')
abline(h=YG_coeffs['male'], col='#D1AC00')
abline(h=YG_coeffs['other'], col='#D1AC00')
```

## Year & Field
```{r}
YF_model <- glm(
      formula = binconcepts ~ 
                firsty + secondy + thirdy + chemistry + textiles + biology + fast + pharma +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(YF_model)

YF_coeffs = coef(YF_model)
boxplot(
  YF_coeffs, 
  xlab='year & field model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#909be9'
) 
abline(h=YF_coeffs['firsty'], col='#909be9')
abline(h=YF_coeffs['secondy'], col='#909be9')
abline(h=YF_coeffs['thirdy'], col='#909be9')
abline(h=YF_coeffs['chemistry'], col='#909be9')
abline(h=YF_coeffs['textiles'], col='#909be9')
abline(h=YF_coeffs['biology'], col='#909be9')
abline(h=YF_coeffs['pharma'], col='#909be9')
abline(h=YF_coeffs['fast'], col='#909be9')
```


# ALL
```{r}
ALL_model <- glm(
      formula = binconcepts ~ 
                french + german + firsty + secondy + thirdy + female + male + other + chemistry + textiles + biology + fast + pharma +
                greengreen_other + greenred_other + notgreennotred_other + noobserved_other +
                greengreen_concentration + greenred_concentration + notgreennotred_concentration + noobserved_concentration +
                greengreen_width + greenred_width + notgreennotred_width + noobserved_width +
                greengreen_wavelength + greenred_wavelength + notgreennotred_wavelength + noobserved_wavelength +
                greengreen_solution + greenred_solution + notgreennotred_solution + noobserved_solution +
                greengreen_pdf + greenred_pdf + notgreennotred_pdf + noobserved_pdf +
                greengreen_break + greenred_break + notgreennotred_break + noobserved_break +
                concentrationlab,
      data = action_count,
      family=binomial
    )
summary(ALL_model)

ALL_coeffs = coef(ALL_model)
boxplot(
  ALL_coeffs, 
  xlab='all model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#cfe2f3'
) 
abline(h=ALL_coeffs['firsty'], col='#cfe2f3')
abline(h=ALL_coeffs['secondy'], col='#cfe2f3')
abline(h=ALL_coeffs['thirdy'], col='#cfe2f3')
abline(h=ALL_coeffs['chemistry'], col='#cfe2f3')
abline(h=ALL_coeffs['textiles'], col='#cfe2f3')
abline(h=ALL_coeffs['biology'], col='#cfe2f3')
abline(h=ALL_coeffs['pharma'], col='#cfe2f3')
abline(h=ALL_coeffs['fast'], col='#cfe2f3')
abline(h=ALL_coeffs['female'], col='#cfe2f3')
abline(h=ALL_coeffs['male'], col='#cfe2f3')
abline(h=ALL_coeffs['other'], col='#cfe2f3')
```





```{r}
singlegg_model <- glm(
      formula = binconcepts ~ 
                greengreen_concentration + greengreen_solution,
      data = action_count,
      family=binomial
    )
summary(singlegg_model)
singlegg_coeffs = coef(singlegg_model)
boxplot(
  singlegg_coeffs, 
  xlab='single model', 
  ylim=c(-20, 50), ylab='coefficient value', col='#7389AE'
)
```

```{r}
general_model <- glmnet(
                x=(as.matrix(action_count[, 3:31])),
                y=as.numeric(unlist(action_count[, 32])),
      alpha=1,
      family=binomial
    )
summary(general_model)
general_coeffs = coef(general_model)
print(general_coeffs[, 10])
```




```{r}
typeof(action_count[,3:31])
```

